MS_Imp_Guidelines

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
minor

Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions. Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia. To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets. Data created for illustration purposes is prominently labelled as not for use in decision-analysis.

>>>>

<!-- Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.  -->

Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia. To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets. Data created for illustration purposes is prominently labelled as not for use in decision-analysis.

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
minor

We became interested in modular and open-source approaches to CHEM development in 2018 when beginning to plan how to synthesise a number of current or planned economic modelling projects in youth mental health in one multi-purpose model. This overarching youth mental health model  is called readyforwhatsnext [@rfwn2024]. Initially we planned to construct readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:

>>>>

We became interested in modular and open-source approaches to CHEM development in 2018 when beginning to plan how to synthesise a number of current or planned economic modelling projects in youth mental health in one multi-purpose model. This overarching youth mental health model  is called readyforwhatsnext [@rfwn2024]. Initially, we plan to construct readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:

### 2024-02-20 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
minor

## Purpose
We decided to develop a software framework to help us address challenges we encountered during the planning and early implementation of readyforwhatsnext. The software framework is called ready4 [@ready424]. The purpose of ready4 is to support the development of CHEMs that meet explicit criteria for transparency, reusability and updatability. We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are: software files are open access, developer contributions are easily identified, programming practices promote selective reuse, licenses restrict only unethical reuse, maintenance infrastructure is in place and new releases are systematically retested, with and deprecation of outdated artefacts.

@@

UR 1) A *template CHEM module* which can be used to create CHEM modules that can: (i) safely share inputs and outputs with each other without impairing any module's integrity; (ii) be run as independent models; and (iii) be selectively replaced, updated or extended.

UR2) *Tools* for creating new CHEM modules from the template module.

UR 3) A simple *syntax* to support consistency in how CHEM modules are used in health economic analysis programs.

UR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.

UR 5) Integration with online open science data archiving services to streamline the *ingesting, labeling and sharing of CHEM data*.

UR 6) Tools to help *author replicable health economic analysis programs and reporting subroutines*.

@@

One library provides the foundation for the ready4 framework. <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].  -->The ready4 foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448]. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment. Encapsulation can be used to help ensure that CHEM modules continue to work as intended when they are combined<!-- [@ready4oop2022] -->. Inheritence allows new CHEM modules to be created that inherit some or all of the properties of a parent module. Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects. Inheritance also facilitates the selective editing of CHEM modules when transferring models to different decision contexts <!-- [@ready4oop2022] -->. The ready4 template CHEM module can therefore be used to create other CHEM modules that inherit common set of properties (meeting *UR 1*). One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *UR 3*). The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *UR 7*) and tools for developing and maintaining a project documentation website (*UR 8*).

>>>>

## Purpose
We decided to develop a software framework to help us address challenges we encountered during the planning and early implementation of readyforwhatsnext. The software framework is called ready4 [@ready424]. The purpose of ready4 is to support the development of CHEMs that meet explicit criteria for transparency, reusability and updatability. We have describe these criteria elsewhere [@ethicsCHEMS2024], but briefly they are: software files are open access, developer contributions are easily identified, programming practices promote selective reuse, licenses restrict only unethical reuse, maintenance infrastructure is in place and new releases are systematically retested, with deprecation of outdated artefacts.

@@

UR 1) A *template* for creating CHEM modules that can: (i) safely share inputs and outputs with each other without impairing any module's integrity; (ii) be run as independent models; and (iii) be selectively replaced, updated or extended.

UR 2) *Developer tools* that integrate with online open source software development services to support streamlined workflows for authoring R libaries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) consistently documented; (iv) licensed for reuse; (v) bundled with citation data specifying authorship, funding source, version number and a Digital Object Identifier (DOI); and (vi) quality assured with publicly available acceptance and unit tests.

UR 3) A simple *syntax* that promotes support consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.

<!-- UR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.  -->

UR 5) *Data management tools* that integrate with online data repository services to streamline the ingesting, labeling and sharing of publicly available and confidential data.

UR 6) *Reporting tools* that include: 
<!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->
(i) replicable health economic analysis programs; and (ii) reporting subroutines that.

@@

One library provides the foundation for the ready4 framework. <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].  -->The ready4 foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448]. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment. Encapsulation can be used to help ensure that CHEM modules continue to work as intended when they are combined<!-- [@ready4oop2022] -->. Inheritence allows new CHEM modules to be created that inherit some or all of the properties of a parent module. Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects. Inheritance also facilitates the selective editing of CHEM modules when transferring models to different decision contexts<!-- [@ready4oop2022] -->. The ready4 template CHEM module can therefore be used to create other CHEM modules that inherit common set of properties (meeting *UR 1*). One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *UR 3*). The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *UR 7*) and tools for developing and maintaining a project documentation website (*UR 8*).
